\vspace{-3em} \textbf{ Mapping stellar surfaces\\ II: An interpretable Gaussian process model for light curves }

### 2021-02-04 paper1/ms.tex
update refs, acknowledgments

While the stellar surfaces are all distinct, containing between one (top)
and six (bottom) large dark spots,
\textbf{their rotational light curves are identical}
(lower panel). This is true even in the absence of measurement
error: the mapping from a stellar surface
to its rotational light curve is so degenerate that there exist an infinite number of solutions
to the inverse problem. This fact has been pointed out recently in different contexts
\citep[e.g.,][]{Cowan2013,Rauscher2018,Luger2019,Basri2020}, but it dates back at least to
\citet{Russell1906}, who demonstrated it by expanding the surface
intensity of a celestial body in terms of spherical harmonics
(see Figure~\ref{fig:ylms}). \citet{Russell1906} showed
that many of the modes comprising the intensity profile of a spherical
object are in the \emph{null space}, the set of surface features that have identically
zero effect on the light curve. In fact, as we will show in \S\ref{sec:nullspace},
the \emph{vast majority} of the modes are in the null space for rotational
light curves of stars. This is what allows us to construct pathological
scenarios like that shown in Figure~\ref{fig:degeneracies}, where the light curve
could be explained by any number of spots atop a heterogeneous bright background.

@@

A direct consequence of this fact is that \textbf{results based on analyses
    of individual light curves are often extremely sensitive to
    the particular assumptions of one's model.} We therefore urge lots of care
in these kinds of analyses, where assumptions of uniform-contrast, discrete, and
circular spots, or alternatively of maximum entropy or ``simplicity'' may
result in significant bias. In this respect, we agree with the recent
paper by \citep{Basri2020}, which cautions against the association of
invidual dips in light curves with individual, discrete spots.

@@

We would like to thank Michael Gully-Santiago and the
Astronomical Data Group at the Center for Computational Astrophysics for
many thought-provoking discussions that helped shape this paper.

>>>>

While the stellar surfaces are all distinct, containing between one (top)
and six (bottom) large dark spots,
\textbf{their rotational light curves are identical}
(lower panel). This is true even in the absence of measurement
error: the mapping from a stellar surface
to its rotational light curve is so degenerate that there exist an infinite number of solutions
to the inverse problem. This fact has been pointed out recently in different contexts
\citep[e.g.,][]{Cowan2013,Rauscher2018,Sandford2019,Luger2019,Basri2020}, but it dates back at least to
\citet{Russell1906}, who demonstrated it by expanding the surface
intensity of a celestial body in terms of spherical harmonics
(see Figure~\ref{fig:ylms}). \citet{Russell1906} showed
that many of the modes comprising the intensity profile of a spherical
object are in the \emph{null space}, the set of surface features that have identically
zero effect on the light curve. In fact, as we will show in \S\ref{sec:nullspace},
the \emph{vast majority} of the modes are in the null space for rotational
light curves of stars. This is what allows us to construct pathological
scenarios like that shown in Figure~\ref{fig:degeneracies}, where the light curve
could be explained by any number of spots atop a heterogeneous bright background.

@@

A direct consequence of this fact is that \textbf{results based on analyses
    of individual light curves are often extremely sensitive to
    the particular assumptions of one's model.} We therefore urge lots of care
in these kinds of analyses, where assumptions of uniform-contrast, discrete, and
circular spots, or alternatively of maximum entropy or ``simplicity'' may
result in significant bias. In this respect, we agree with the recent
paper by \citet{Basri2020}, which cautions against the association of
invidual dips in light curves with individual, discrete spots.

@@

We would like to thank Michael Gully-Santiago, Fran Bartoli\'c, and the
Astronomical Data Group at the Center for Computational Astrophysics for
many thought-provoking discussions that helped shape this paper.

### 2021-02-04 paper2/ms.tex
update refs, acknowledgments

We would like to thank David W. Hogg, Michael Gully-Santiago, Adam Jermyn,
Megan Bedell, and the
Astronomical Data Group at the Center for Computational Astrophysics for
many thought-provoking discussions that helped shape this paper.

>>>>

We would like to thank David W. Hogg, Michael Gully-Santiago, Adam Jermyn,
Megan Bedell, Dylan Simon, and the
Astronomical Data Group at the Center for Computational Astrophysics for
their help and for
many thought-provoking discussions that made this paper possible.
